---
title: "N-Mixture Models"
author: "Document Author"
date: "December 2020"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---






# Packages, links, pubs, etc.


## Packages

unmarked - https://www.rdocumentation.org/packages/unmarked/versions/1.0.1/topics/unmarked-package

- tools for modeling unmarked animal data


## Pubs

- Christine C. Rega-Brodsky and Charles H. Nilon, “Forest Cover Is Important across Multiple Scales for Bird Communities in Vacant Lots,” Urban Ecosystems 20, no. 3 (June 1, 2017): 561–71, https://doi.org/10.1007/s11252-016-0614-5.
  - Example paper sent by Sebastian Moreno.
  - Doesn't include data or R code in supplemental materials.
  - Used R package `unmarked` and PC-ORD
  


## Online resources

### WFA8433 - Course by Michael Colvin

- n-mixture model session https://mcolvin.github.io/WFA8433/Class-18.html
- https://mcolvin.github.io/WFA8433/syllabus.html


### N-Mixture models tutorial (en español)

- https://jabiologo.github.io/web/tutorials/nmixture.html



## David Zeleney

- https://www.davidzeleny.net/anadat-r/doku.php/en:ordiagrams#types_of_ordination_plots


## A New Output Format

`html_pretty` in the [**prettydoc**](https://github.com/yixuan/prettydoc/)
package is a new output format for creating HTML documents from R Markdown files.
`html_pretty` is more lightweight compared to `html_document`, and is more
stylish than `html_vignette` when creating package vignettes.

## New Styles

`html_pretty` currently supports three page themes (`cayman`, `tactile` and
`architect`), and two syntax highlight styles (`github` and `vignette`).
The theme and highlight styles can be specified in the document metadata,
for example:

```yaml
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
```

## Your Familiar Tools

Feel free to use the `knitr` infrastructure with dozens of tunable options in
your document.

```{r fig.width=6, fig.height=6, fig.align='center'}
set.seed(123)
n <- 1000
x1  <- matrix(rnorm(n), ncol = 2)
x2  <- matrix(rnorm(n, mean = 3, sd = 1.5), ncol = 2)
x   <- rbind(x1, x2)
head(x)
smoothScatter(x, xlab = "x1", ylab = "x2")
```

You can include code snippets of languages other than R, but note that
the block header has no curly brackets around the language name.

```cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can also write math expressions, e.g. $Y = X\beta + \epsilon$,
footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(iris, 10))
```

## Stay Tuned

Please visit the [development page](https://github.com/yixuan/prettydoc/) of the 
`prettydoc` package for latest updates and news. Comments, bug reports and
pull requests are always welcome.
